\documentclass{article}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{float}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage[labelfont=bf]{caption}
\usepackage[left=0.75in, top=1in, right=0.75in, bottom=1in]{geometry}
\pagestyle{plain}
\begin{document}
\rhead{Aaron Okano, Jason Wong\\
       ECS 152B, Winter 2013\\
       Assignment 1}
\thispagestyle{fancy}
\vspace*{12pt}

% Start writing here

\section*{Problem 1}


\section*{Problem 2}

\begin{enumerate}[label={\bf (\alph*)}]
  \item \verb=100000001011010000011000000100010100000011100000001=
  \item \verb=01001100000000=
\end{enumerate}

\section*{Problem 3}

\begin{enumerate}[label={\bf (\alph*)}]
  \item \verb=--1-011-001= $\rightarrow$ \verb=10100111001=
  \item Syndrome: \verb=010=. The second bit is incorrect.
\end{enumerate}

\section*{Problem 4}

If the CRC were appended as a header, it would need to be computed before the
message is sent onto the link. By attaching it to the end, we can compute the
CRC while transmitting the message.

\section*{Problem 5}

We can easily compute the round-trip time for a single packet-acknowledgement
sequence by adding up the transmission and propagation delays (we are ignoring
the processing and queueing delays):
\begin{equation*}
  \text{rtt} = d_{mt} + d_{mp} + d_{at} + d_{ap}
\end{equation*}
where $d_{mt}$ is the transmission delay for the message packet, $d_{mp}$ is the
propagation delay for the packet, and likewise for the acknowledgement. We can
now make the observation that transmission delay is $b/C$ and the propagation
delay for both the file packets and the acknowledgement packets
is $d\cdot5\times 10^{-6}$. The equation now becomes
\begin{equation*}
  \text{rtt} = \frac{b}{C} + \frac{100}{C} + 10\cdot d\times 10^{-6}
\end{equation*}

This is only for a single packet, but we can multiply it by the number of
packets, $10^6 / b$, to find the total time for the whole file.
\begin{equation*}
  \text{time} = \frac{10^6}{b} \cdot \text{rtt}
\end{equation*}

Total bits transmitted is the size of the file plus the number of
acknowledgement bits sent: $10^6 + 10^8/b$. Assuming throughput includes bits
from ACKs.

\begin{enumerate}[label={\bf (\alph*)}]

  \item $\text{rtt} = 10^{-4} + 10^{-5} + 10^{-4}$.
    Now, multiply by the number of packets: $10^4 \text{rtt} = 1 + 0.1 +
    1 = 2.1 s$. The throughput is $(10^6 + 10^6) / 2.1 \approx 952$ kbps.
  \item $\text{rtt} = 2\times 10^{-5} + 10^{-5} = 3\times 10^{-5}$. Multiplying
    by number of packets ($10^4$ again) yields a total time of 0.3 seconds.
    Throughput is $(10^6 + 10^6) / 0.3 \approx 6.67$ Mbps.
  \item $\text{rtt} = 2\cdot 10^{-4} + 2\cdot 10^{-5}$. Multiply by number of
    packets, once again $10^4$, yields 2.2 seconds for the total time.
    Throughput is $(2\cdot10^6)/2.2 \approx 909$ kbps.
  \item $\text{rtt} = 2\cdot10^{-4} + 2\cdot 10^{-6} + 2\cdot 10^{-6}$. Total
    time is $100\cdot \text{rtt} = 2\cdot10^{-2} + 4\cdot10^{-4} \approx 0.0204$
    seconds. Throughput is $(10^6 + 10^4)/0.0204 \approx 49.5$ Mbps.

\end{enumerate}

\section*{Problem 6}



\section*{Problem 7}

\end{document}
